Proposal to improve BBC Search through the use of Linked Data

### 2014-05-04 chapter2.tex
Nearing the end of chapter 2.

\section{Linked Enterprise Data}

@@

\section{Reasoning and Inference}

>>>>

Evaluation of the effectiveness of search results enhanced with rich snippets
via both explicit and implicit user feedback had been carried out by
Haas et al.\cite{haas2011enhanced} at Microsoft and Yahoo! research. The
results showed a promising preference from 84\% of users for a result
with enhanced information with the most common downside being that the
snippet may sometimes present incorrect information (e.g. showing the wrong
price for a product is less preferable than simply not attempting to present
the price at all). Implicit feedback via click-through rates (CTR) --
a common metric to indicate that users are happy enough with the information
given to click on the link given -- suggested users were more likely to
follow enhanced results.

A higher CTR for semantically-enhanced search results creates some pressure
and incentive on web publishers to include semantic metadata in their web
content if they aspire to attacting visitors via global search engines such
as Google, Bing and Yahoo!.

In section~\ref{linked-enterprise-data} and section~\ref{reasoning}, I will
outline some of the linked data approaches and techniques that relate to
working with data models themselves.

\section{Linked Enterprise Data}
\label{linked-enterprise-data}

@@

\section{Reasoning and Inference}
\label{reasoning}
